Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-11 ch04-lrmhinf/ch04appendices.inc.tex
Add figure to illustrate SNR

\section{\glsentrytext{AVIS} Measurement set-up}
\label{app:avis-setup}
The measurements of the \gls{AVIS} are carried out using a \Simulink model running at a sampling time of $\Ts = 1\unit{ms}$ as shown in \figref{fig:avis:simulink:setup} and \figref{fig:avis:simulink:avis}.

>>>>

\section{\glsentrytext{AVIS} Measurement set-up}
\label{app:avis-setup}
The measurements of the \gls{AVIS} are carried out using a \Simulink model that configures the \gls{DAQ} card, implements a digital controller and processes the signals.
\Simulink executes the code, as shown in \figref{fig:avis:simulink:setup} and \figref{fig:avis:simulink:avis},  using a constant time step $\Ts = 1\unit{ms}$ on a real-time computer running \code{xPC Target} (nowadays: \Simulink Real-Time) equiped with a Quanser Q8 \gls{DAQ} card that is connected to the physical \gls{AVIS} setup.

### 2016-04-11 ch04-lrmhinf/lrmhinf.tex
Add figure to illustrate SNR

\disclaimer{
The \gls{LRM} and \gls{LPM} are described in \chapref{sec:nonparametric} and \citep{Schoukens2009LPM,Pintelon2010LPM1,Pintelon2010LPM2,McKelvey2012LRM} in more detail.
Below, we give briefly re-iterate some pertinent aspects and notations.
}

@@

\begin{guideline}[Measure $4$ to $5\timeconst$ to observe its peak value using the local models]
After $4$ to $5$ time constants of the dominant pole, the local models offer a reliable insight into the peak value of a transfer function when a sufficient \gls{SNR} of approximately $20\unit{dB}$ is available such that the \gls{LRM} can be used.
For purely \gls{FRF}-based estimates, on the other hand, the measurement only attains similar performance when measuring for $20\timeconst$.
\end{guideline}

>>>>

\disclaimer{
The \gls{LRM} and \gls{LPM} are described in \chapref{sec:nonparametric} and \citep{Schoukens2009LPM,Pintelon2010LPM1,Pintelon2010LPM2,McKelvey2012LRM} in more detail.
Below, we briefly re-iterate some pertinent aspects and notations.
}

@@

\begin{guideline}[Measure $4$ to $5\timeconst\,$ to observe its peak value using the local models]
\begin{minipage}{0.725\textwidth}
After $4$ to $5$ time constants of the dominant pole, the local models offer a reliable insight into the peak value of a transfer function when a sufficient \gls{SNR} of approximately $20\unit{dB}$ is available such that the \gls{LRM} can be used.
For purely \gls{FRF}-based estimates, on the other hand, the measurement only attains similar performance when measuring for $20\timeconst$.
\end{minipage}
\hfill
\begin{minipage}{0.25\textwidth}
\setlength\figurewidth{\columnwidth}
\setlength\figureheight{0.618\figurewidth}
\input{\thisDir/figs/sketch-SNR.tikz}
\end{minipage}
\end{guideline}
